---
title: "Visualizing power calculations"
author: "Diego Costa"
date: "July 13, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description

- This is a reproducible pitch presentation for the Data Products Course Project.
- Have you ever wondered how the variables distribution look like when performing power calculations?
- Wonder no more, with my App you can visualize it perfectly. 


## What does it do

- It plots the kernel density for two random t distributions
- It performs a power calculation for the difference of given means
- *It assumes a two-sample and two-sided t test will be done*

## Inputs

- Enter two means to compare (red and blue).
- Enter your sample size.
- Enter the desired alpha error.
- Enter the estimated standard deviation.

## Example output

#### Mean A = 60
#### Mean B = 70
#### Sample size = 80, SD = 20, alpha = 0.05 
```{r, echo = FALSE}
p <- power.t.test(80, 10, sd = 20, sig.level = 0.05, type = "two.sample")
```
#### Calculated power = `r p$power`
```{r, echo = FALSE}
plot(density(rt(80, 79, 60)), col = "red", main = "Kernel density plot for random t distributions" , xlab = "", ylab = "")
lines(density(rt(80, 79, 70)), col = "blue")
p <- power.t.test(80, 10, sd = 20, sig.level = 0.05, type = "two.sample")
text(labels(p$power))
```




